Bayesian Hyper-Heuristics

### 2023-02-04 article/sections/08-results.tex
🚧 (article): WIP save point for revision

This section provides the results of all the experiments that have been conducted. Detailed discussions follow on the outcomes of each experiment. Discussions are accompanied by figures and plots to help provide visual aid for discussions. The output of the statistical analysis that yielded the results is provided in Appendix \ref{app:statistical_analysis}.

@@

Given the nature of the \acs{BHH}, it is recommended that the following aspects be kept in mind when observing the results. The \acs{BHH} applies a form of online learning. As such, the \acs{BHH} applies the learning mechanism during training in a single run of the training process. The training process is not repeated iteratively. All experiments conducted are executed for 30 epochs. The number of training steps executed is dependent on the batch size applied for each dataset.

All of the underlying \acp{FFNN} trained in the empirical process are relatively small. As such, most of the training progress is observed to occur within the first five epochs. As a result, the \acs{BHH} should apply most learning at the early stages of the training process. After five epochs, the training of most of the underlying \acp{FFNN} converges and little performance gain is observed after that point. Since this empirical process does not apply early stopping of the training process, the \acs{BHH} will continue to explore the heuristic space beyond the five epoch mark.

@@

This section provides the empirical results of the case study on the behaviour of the \acs{BHH} as it is used to train a \acs{FFNN} on the iris dataset. As a reminder, the iris dataset contains 150 records, split into a training dataset containing 120 records, and a test dataset that contains 30 records. The test dataset is treated like a validation dataset, and is evaluated at every training step to illustrate the outcomes of the \acs{BHH} throughout the training process. Mini-batch training is executed with a batch size of 30. The results that are presented are averaged over 30 independent runs.

The case study focuses on three variants of the \acs{BHH}. These include the baseline configuration, as was provided in Section \ref{sec:bhh} and is denoted as bhh\_baseline (illustrated throughout in \textcolor{red}{red}). Furthermore, the case study also includes a configuration of the \acs{BHH} that has a ``long memory'' by setting the \textit{replay window size} hyper-parameter to 250, and is denoted as bhh\_replay\_250 (illustrated throughout in \textcolor{green}{green}). Finally, the case study includes a configuration that makes use of the \textit{symmetric} credit assignment strategy hyper-parameter, and is denoted as bhh\_credit\_symmetric (illustrated throughout in \textcolor{blue}{blue}).

These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level heuristics in the heuristic pool, and the configuration that utilises the symmetric credit assignment strategy is chosen to illustrate a case where there \acs{BHH} does not reward good performance, and does not yield a bias towards heuristics that perform well at all.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% METRICS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Performance Metrics}\label{sec:results:case_study:performance_metrics}

@@

Although the different configurations of the \acs{BHH} are all able to successfully train the underlying \acs{FFNN}, in this particular case, there is no clear distinction between the performance of any of the configurations under consideration.

The volatility and minor divergence of the test loss compared to the training loss, observed in Figure \ref{fig:results:case_study:metrics:test_loss}, is due to overfitting and partly due to the noisiness that results from mini-batch training. Early stopping can be applied to the training process to halt training before the model overfits on the training data. The training dataset is also very small, with just 120 samples. Furthermore, a very small batch size of 16 is used. As such, noisiness and overfitting can be expected.

From Figure \ref{fig:results:case_study:metrics:train_loss}, at the 22nd epoch, a small divergence of the train loss can be observed. This could simply be a result of momentum that is maintained when switching between low-level heuristics in an attempt to find better solutions. For example, momentum can be built up by one of the gradient-based heuristics, after which the \acs{BHH} switches to another heuristic in an attempt to find better solutions. The \acs{BHH} does not incorporate a \textit{move-acceptance strategy}, whereby a heuristic's outcome is rejected if it does not improve on previous solutions, yielding a possibly worse loss measurement as it relates to the test set. A move-acceptance strategy can be utilised on a validation set as a mechanism to accept or reject heuristic progressions from one step to the other.

Finally, it should be noted that the \acs{BHH} implements learning at every mini-batch step, while Figure \ref{fig:results:case_study:metrics} only provides the outcomes of performance metrics at the end of each epoch. Further investigation is required at a mini-batch step level and is provided in the following sections.

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % PARAMS ALPHAS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Concentration Parameters}\label{sec:results:case_study:concentration_parameters}

@@

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[0].pdf}
		\caption{$\alpha_{0}$ - \acs{SGD}}
		\label{fig:results:case_study:alphas:0}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[6].pdf}
		\caption{$\alpha_{6}$ - \acs{Adam}}
		\label{fig:results:case_study:alphas:6}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[7].pdf}
		\caption{$\alpha_{7}$ - \acs{PSO}}
		\label{fig:results:case_study:alphas:7}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[8].pdf}
		\caption{$\alpha_{8}$ - \acs{GA}}
		\label{fig:results:case_study:alphas:8}
	\end{subfigure}
	\par\bigskip
	\caption{The average value of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:alphas}
\end{figure}

The first logical observation to be made from Figures \ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} is the step-wise, increasing nature of $\boldsymbol{\alpha}$ for the bhh\_replay\_250 configuration, illustrated in \textcolor{green}{green}. Since the replay window size is sufficiently large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics at all. The value for $\boldsymbol{\alpha}$ is never reset to its initial value of 1.0, and thus, $\boldsymbol{\alpha}$ continues to increase throughout the training process. However, it should be noted that the rate and degree of change is different for different indices of $\boldsymbol{\alpha}$. The aforementioned observation is the first indicator of the learning process yielded by the \acs{BHH}. Heuristics that perform well will see their corresponding element in $\boldsymbol{\alpha}$ increase more rapidly than other heuristics that do not perform well.

@@

Notice from Figure \ref{fig:results:case_study:alphas} that $\boldsymbol{\alpha} \geq 1.0$ for multiple elements. This is due to the accumulation of pseudo counts for $\boldsymbol{\alpha}$ by the Bayesian analysis process. Furthermore, this is also because the same heuristic can be allocated to multiple entities, each contributing a minimum pseudo-count gain of 1.0 to the corresponding element in $\boldsymbol{\alpha}$ through the Bayesian analysis process.

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % PARAMS THETAS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Probability Distribution of Heuristic Selection Probabilities}\label{sec:results:case_study:probs_of_select_probs}

This section provides a detailed investigation into the \textit{probability distribution of heuristic selection probabilities} as it changes throughout the training process. As a reminder, the \acs{BHH} implements a Bayesian view of probabilistic modelling and thus, heuristic selection probabilities are defined by an underlying probabilistic distribution themselves. The probability distribution of heuristic selection probabilities is denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, where $\boldsymbol{\theta} \sim Dir(\boldsymbol{\alpha, K})$ are the sampled heuristic selection probabilities.

@@

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[0].pdf}
		\caption{P($\theta_{0} \vert \alpha_{0})$ - \acs{SGD}}
		\label{fig:results:case_study:thetas:0}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
		\caption{P($\theta_{6} \vert \alpha_{6})$ - \acs{Adam}}
		\label{fig:results:case_study:thetas:6}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[7].pdf}
		\caption{P($\theta_{7} \vert \alpha_{7})$ - \acs{PSO}}
		\label{fig:results:case_study:thetas:7}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[8].pdf}
		\caption{P($\theta_{8} \vert \alpha_{8})$ - \acs{GA}}
		\label{fig:results:case_study:thetas:8}
	\end{subfigure}
	\par\bigskip
	\caption{The average sampled heuristic selection probabilities, denoted $\boldsymbol{\theta}$, at indices 0, 6, 7, and 8. The heuristic selection probabilities are sampled from the probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:thetas}
\end{figure}

@@

Another observation to make occurs in the first 30 steps of the training process. In Figure \ref{fig:results:case_study:thetas}, notice how all three configurations mostly yield the same heuristic selection probabilities in these first 30 steps. This can be explained as follows: all three configurations use a different random seed per run, but use the same random seed across configurations for the same run number. This is done so that any difference in the behaviour of the different \acs{BHH} configurations are then not a result of random sampling, but solely because of differences in their approaches. This is especially applicable to the initialisation process, where entities are randomly placed in the search space, as well as the early stages of training, where most of the training progress is made.

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % PARAMS P_H (Priors)
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Prior Heuristic Selection Probabilities}\label{sec:results:case_study:prior_selec_prob}

This section provides a brief investigation into the \textit{prior heuristic selection probabilities} that result from the probabilistic model implemented by the \acs{BHH}. The prior heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$. As such, $P(\boldsymbol{H} \vert \boldsymbol{\theta}) = \boldsymbol{\theta}$ and heuristics are initially sampled such that $\boldsymbol{H} \sim Cat(\boldsymbol{\theta})$.

@@

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[0].pdf}
		\caption{P($h_{0} \vert \theta_{0})$ - \acs{SGD}}
		\label{fig:results:case_study:p_H:0}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
		\caption{P($h_{6} \vert \theta_{6})$ - \acs{Adam}}
		\label{fig:results:case_study:p_H:6}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[7].pdf}
		\caption{P($h_{7} \vert \theta_{7})$ - \acs{PSO}}
		\label{fig:results:case_study:p_H:7}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[8].pdf}
		\caption{P($h_{8} \vert \theta_{8})$ - \acs{GA}}
		\label{fig:results:case_study:p_H:8}
	\end{subfigure}
	\par\bigskip
	\caption{The average prior heuristic selection probabilities, $P(\boldsymbol{H} \vert \boldsymbol{\theta})$, at indices 0, 6, 7, and 8. The prior heuristic selection probabilities are sampled from the probability distribution of heuristic selection probabilities, denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_H}
\end{figure}

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % PARAMS P_HgEC (Posterior)
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Posterior Heuristic Selection Probabilities}\label{sec:results:case_study:posterior_selec_prob}

This section provides a detailed discussion on the outcomes of the \textit{posterior heuristic selection probabilities}. These posterior heuristic selection probabilities form the basis of the probabilistic model implemented by the \acs{BHH}. The posterior heuristic selection probability distribution is defined as $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, where $\boldsymbol{E}$ represents the vector of entities in the entity pool, and $\boldsymbol{C}$ represents the vector of credit allocation outcomes as implemented by the credit assignment strategy. Furthermore $\boldsymbol{\theta}$ and $\boldsymbol{\phi}$ represent the probability distributions of heuristic selection probabilities and the entity selection probabilities respectively. Finally, $\boldsymbol{\psi}$ represents the probability distribution of successful credit allocation probabilities.

@@

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][0].pdf}
		\caption{$P(h_{0} \vert e_{0}, c_{1})$ - \acs{SGD}}
		\label{fig:results:case_study:p_HgEC:0:0}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
		\caption{$P(h_{6} \vert e_{0}, c_{1})$ - \acs{Adam}}
		\label{fig:results:case_study:p_HgEC:0:6}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][7].pdf}
		\caption{$P(h_{7} \vert e_{0}, c_{1})$ - \acs{PSO}}
		\label{fig:results:case_study:p_HgEC:0:7}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][8].pdf}
		\caption{$P(h_{8} \vert e_{0}, c_{1})$ - \acs{GA}}
		\label{fig:results:case_study:p_HgEC:0:8}
	\end{subfigure}
	\par\bigskip
	\caption{The average calculated proportional posterior heuristic selection probabilities for heuristics $(\boldsymbol{H})$ at indices 0, 6, 7, and 8, given the application to entity $e_{0}$ and requiring a successful credit allocation, $c_{1}$, from the \textit{ibest} credit assignment strategy. The proportional posterior heuristic selection probabilities are calculated from the probabilistic model, denoted $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, over 240 steps, and obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:p_HgEC:0}
\end{figure}

@@

\begin{sidewaystable}[htbp]
	\centering
	\caption{Empirical results showing test loss and statistics for different low-level heuristics compared to three heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs, measured at the last epoch.}
	\label{tab:results:standalone:metrics:loss}%
	\par\bigskip
	\resizebox{\textwidth}{!}{
		\begin{tabular}{r|lll|l|l|l|l|l|lllll}
			                                    & \multicolumn{13}{c}{\textbf{BHH vs. Low-Level Heuristics - Average Test Loss}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         \\
			\cmidrule{2-14}    \textbf{dataset} & \multicolumn{1}{c}{\textbf{adagrad}}                                           & \multicolumn{1}{c}{\textbf{adam}}                       & \multicolumn{1}{c|}{\textbf{rmsprop}}                   & \multicolumn{1}{c|}{\textbf{bhh\_gd}}                   & \multicolumn{1}{c|}{\textbf{nag}}                       & \multicolumn{1}{c|}{\textbf{bhh\_all}}                  & \multicolumn{1}{c|}{\textbf{adadelta}}                  & \multicolumn{1}{c|}{\textbf{bhh\_mh}}                   & \multicolumn{1}{c}{\textbf{ga}}                         & \multicolumn{1}{c}{\textbf{pso}}                        & \multicolumn{1}{c}{\textbf{sgd}}                        & \multicolumn{1}{c}{\textbf{momentum}}                   & \multicolumn{1}{c}{\textbf{de}}                         \\
			\midrule
			\textbf{abalone}                    & \cellcolor[rgb]{ .506,  .776,  .486}1.9678 ($\pm$0.032)                        & \cellcolor[rgb]{ .494,  .773,  .486}1.9651 ($\pm$0.035) & \cellcolor[rgb]{ .388,  .745,  .482}1.9455 ($\pm$0.035) & \cellcolor[rgb]{ .749,  .847,  .502}2.0125 ($\pm$0.068) & \cellcolor[rgb]{ .765,  .851,  .502}2.0156 ($\pm$0.035) & \cellcolor[rgb]{ 1,  .922,  .518}2.0587 ($\pm$0.088)    & \cellcolor[rgb]{ .788,  .859,  .502}2.0199 ($\pm$0.034) & \cellcolor[rgb]{ .996,  .827,  .502}2.2942 ($\pm$0.055) & \cellcolor[rgb]{ .984,  .612,  .459}2.8155 ($\pm$0.055) & \cellcolor[rgb]{ .98,  .522,  .443}3.0384 ($\pm$0.294)  & \cellcolor[rgb]{ .992,  .773,  .49}2.428 ($\pm$0.029)   & \cellcolor[rgb]{ .992,  .745,  .486}2.4942 ($\pm$0.029) & \cellcolor[rgb]{ .973,  .412,  .42}3.2959 ($\pm$0.016)  \\
			\textbf{air quality}                & \cellcolor[rgb]{ .651,  .82,  .494}0.2569 ($\pm$0.007)                         & \cellcolor[rgb]{ .827,  .871,  .506}0.2606 ($\pm$0.009) & \cellcolor[rgb]{ .388,  .745,  .482}0.2513 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.2642 ($\pm$0.011)    & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .996,  .827,  .502}0.2729 ($\pm$0.016) & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .976,  .914,  .514}0.2637 ($\pm$0.007) & \cellcolor[rgb]{ .996,  .792,  .494}0.2759 ($\pm$0.008) & \cellcolor[rgb]{ .984,  .608,  .459}0.2923 ($\pm$0.023) & \cellcolor[rgb]{ .988,  .69,  .475}0.2852 ($\pm$0.015)  & \cellcolor[rgb]{ .984,  .604,  .459}0.2929 ($\pm$0.016) & \cellcolor[rgb]{ .973,  .412,  .42}0.3097 ($\pm$0.017)  \\
			\textbf{bank}                       & \cellcolor[rgb]{ .459,  .765,  .486}0.2096 ($\pm$0.005)                        & \cellcolor[rgb]{ .4,  .745,  .482}0.2065 ($\pm$0.004)   & \cellcolor[rgb]{ .388,  .745,  .482}0.2058 ($\pm$0.006) & \cellcolor[rgb]{ .588,  .8,  .49}0.2164 ($\pm$0.005)    & \cellcolor[rgb]{ .588,  .8,  .49}0.2164 ($\pm$0.006)    & \cellcolor[rgb]{ 1,  .886,  .514}0.2456 ($\pm$0.065)    & \cellcolor[rgb]{ .627,  .812,  .494}0.2186 ($\pm$0.004) & \cellcolor[rgb]{ .996,  .839,  .502}0.2562 ($\pm$0.011) & \cellcolor[rgb]{ .988,  .686,  .475}0.2881 ($\pm$0.013) & \cellcolor[rgb]{ .973,  .412,  .42}0.3454 ($\pm$0.034)  & \cellcolor[rgb]{ 1,  .922,  .518}0.2382 ($\pm$0.006)    & \cellcolor[rgb]{ 1,  .922,  .518}0.2386 ($\pm$0.005)    & \cellcolor[rgb]{ .976,  .424,  .424}0.3437 ($\pm$0.028) \\
			\textbf{bike}                       & \cellcolor[rgb]{ .388,  .745,  .482}0.0458 ($\pm$0.002)                        & \cellcolor[rgb]{ .592,  .804,  .494}0.0682 ($\pm$0.068) & \cellcolor[rgb]{ 1,  .922,  .518}0.1123 ($\pm$0.103)    & \cellcolor[rgb]{ .467,  .765,  .486}0.0545 ($\pm$0.005) & \cellcolor[rgb]{ .882,  .886,  .51}0.0995 ($\pm$0.002)  & \cellcolor[rgb]{ .565,  .796,  .49}0.0651 ($\pm$0.02)   & \cellcolor[rgb]{ .588,  .8,  .49}0.0679 ($\pm$0.002)    & \cellcolor[rgb]{ 1,  .902,  .514}0.1179 ($\pm$0.006)    & \cellcolor[rgb]{ .992,  .761,  .486}0.1531 ($\pm$0.005) & \cellcolor[rgb]{ .992,  .773,  .49}0.1503 ($\pm$0.025)  & \cellcolor[rgb]{ .992,  .733,  .482}0.1599 ($\pm$0.003) & \cellcolor[rgb]{ .992,  .725,  .482}0.1614 ($\pm$0.003) & \cellcolor[rgb]{ .973,  .412,  .42}0.2399 ($\pm$0.04)   \\
			\textbf{car}                        & \cellcolor[rgb]{ .729,  .843,  .502}0.2027 ($\pm$0.018)                        & \cellcolor[rgb]{ .388,  .745,  .482}0.0972 ($\pm$0.024) & \cellcolor[rgb]{ .408,  .749,  .482}0.1039 ($\pm$0.031) & \cellcolor[rgb]{ .62,  .812,  .494}0.169 ($\pm$0.025)   & \cellcolor[rgb]{ .867,  .882,  .51}0.2454 ($\pm$0.029)  & \cellcolor[rgb]{ .58,  .8,  .49}0.1572 ($\pm$0.034)     & \cellcolor[rgb]{ 1,  .922,  .518}0.2859 ($\pm$0.027)    & \cellcolor[rgb]{ .992,  .733,  .482}0.4891 ($\pm$0.077) & \cellcolor[rgb]{ .98,  .502,  .439}0.7374 ($\pm$0.063)  & \cellcolor[rgb]{ .988,  .667,  .471}0.5632 ($\pm$0.158) & \cellcolor[rgb]{ .98,  .533,  .443}0.7035 ($\pm$0.052)  & \cellcolor[rgb]{ .98,  .506,  .439}0.7322 ($\pm$0.043)  & \cellcolor[rgb]{ .973,  .412,  .42}0.8332 ($\pm$0.074)  \\
			\textbf{diabetic}                   & \cellcolor[rgb]{ .694,  .831,  .498}0.8895 ($\pm$0.004)                        & \cellcolor[rgb]{ 1,  .898,  .514}0.9193 ($\pm$0.01)     & \cellcolor[rgb]{ .918,  .894,  .51}0.8957 ($\pm$0.004)  & \cellcolor[rgb]{ .98,  .914,  .514}0.8976 ($\pm$0.011)  & \cellcolor[rgb]{ .388,  .745,  .482}0.8809 ($\pm$0.004) & \cellcolor[rgb]{ .973,  .412,  .42}1.2983 ($\pm$0.66)   & \cellcolor[rgb]{ .49,  .773,  .486}0.8839 ($\pm$0.005)  & \cellcolor[rgb]{ 1,  .902,  .518}0.9137 ($\pm$0.008)    & \cellcolor[rgb]{ .996,  .843,  .506}0.9613 ($\pm$0.007) & \cellcolor[rgb]{ .996,  .835,  .502}0.9661 ($\pm$0.016) & \cellcolor[rgb]{ .976,  .914,  .514}0.8974 ($\pm$0.004) & \cellcolor[rgb]{ 1,  .922,  .518}0.898 ($\pm$0.003)     & \cellcolor[rgb]{ .988,  .694,  .475}1.0774 ($\pm$0.039) \\
			\textbf{fish toxicity}              & \cellcolor[rgb]{ .588,  .8,  .49}0.0991 ($\pm$0.008)                           & \cellcolor[rgb]{ .451,  .761,  .482}0.0972 ($\pm$0.007) & \cellcolor[rgb]{ .388,  .745,  .482}0.0963 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .91,  .518}0.1056 ($\pm$0.008)     & \cellcolor[rgb]{ .831,  .871,  .506}0.1023 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.1046 ($\pm$0.008)    & \cellcolor[rgb]{ .773,  .855,  .502}0.1016 ($\pm$0.009) & \cellcolor[rgb]{ .976,  .914,  .514}0.1043 ($\pm$0.009) & \cellcolor[rgb]{ 1,  .863,  .506}0.1093 ($\pm$0.009)    & \cellcolor[rgb]{ 1,  .855,  .506}0.1099 ($\pm$0.012)    & \cellcolor[rgb]{ .976,  .475,  .435}0.1393 ($\pm$0.012) & \cellcolor[rgb]{ .973,  .412,  .42}0.1441 ($\pm$0.012)  & \cellcolor[rgb]{ .992,  .733,  .482}0.1193 ($\pm$0.013) \\
			\textbf{forest fires}               & \cellcolor[rgb]{ 1,  .922,  .518}0.0643 ($\pm$0.04)                            & \cellcolor[rgb]{ .557,  .792,  .49}0.0527 ($\pm$0.039)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0626 ($\pm$0.039)    & \cellcolor[rgb]{ .824,  .871,  .506}0.0586 ($\pm$0.034) & \cellcolor[rgb]{ .851,  .878,  .506}0.0592 ($\pm$0.032) & \cellcolor[rgb]{ 1,  .89,  .514}0.081 ($\pm$0.069)      & \cellcolor[rgb]{ .388,  .745,  .482}0.0488 ($\pm$0.032) & \cellcolor[rgb]{ .976,  .914,  .514}0.0621 ($\pm$0.038) & \cellcolor[rgb]{ .553,  .792,  .49}0.0526 ($\pm$0.026)  & \cellcolor[rgb]{ 1,  .914,  .518}0.0692 ($\pm$0.047)    & \cellcolor[rgb]{ .992,  .722,  .482}0.1806 ($\pm$0.008) & \cellcolor[rgb]{ .992,  .706,  .478}0.1885 ($\pm$0.01)  & \cellcolor[rgb]{ .973,  .412,  .42}0.3598 ($\pm$0.09)   \\
			\textbf{housing}                    & \cellcolor[rgb]{ .518,  .78,  .486}0.0889 ($\pm$0.012)                         & \cellcolor[rgb]{ .404,  .749,  .482}0.0848 ($\pm$0.011) & \cellcolor[rgb]{ .388,  .745,  .482}0.0842 ($\pm$0.015) & \cellcolor[rgb]{ .69,  .831,  .498}0.0951 ($\pm$0.015)  & \cellcolor[rgb]{ .612,  .808,  .494}0.0923 ($\pm$0.016) & \cellcolor[rgb]{ .663,  .824,  .498}0.0941 ($\pm$0.017) & \cellcolor[rgb]{ 1,  .922,  .518}0.106 ($\pm$0.019)     & \cellcolor[rgb]{ 1,  .867,  .51}0.1169 ($\pm$0.019)     & \cellcolor[rgb]{ .996,  .812,  .498}0.1279 ($\pm$0.02)  & \cellcolor[rgb]{ .992,  .722,  .482}0.1452 ($\pm$0.03)  & \cellcolor[rgb]{ .984,  .576,  .455}0.1735 ($\pm$0.023) & \cellcolor[rgb]{ .984,  .588,  .455}0.1713 ($\pm$0.018) & \cellcolor[rgb]{ .973,  .412,  .42}0.2057 ($\pm$0.036)  \\

>>>>

This section provides the results of all the experiments that have been conducted. Detailed discussions follow on the outcomes of each experiment. Discussions are accompanied by figures and plots to help provide visual aid for discussions.

@@

The \acs{BHH} applies a form of online learning. As such, the \acs{BHH} applies the learning mechanism during training in a single run of the training process. The training process is not repeated iteratively. All experiments conducted are executed for 30 epochs.

Most of the training progress is observed to occur within the first five epochs. As a result, the \acs{BHH} should apply most learning at the early stages of the training process. After five epochs, the training of most of the underlying \acp{FFNN} converges and little performance gain is observed after that point. Since this empirical process does not apply early stopping of the training process, the \acs{BHH} will continue to explore the heuristic space beyond the five epoch mark.

@@

@@

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[6].pdf}
		\caption{$\alpha_{6}$ - \acs{Adam}}
		\label{fig:results:case_study:alphas:6}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/thetas/theta[6].pdf}
		\caption{P($\theta_{6} \vert \alpha_{6})$ - \acs{Adam}}
		\label{fig:results:case_study:thetas:6}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_H/p_H[6].pdf}
		\caption{P($h_{6} \vert \theta_{6})$ - \acs{Adam}}
		\label{fig:results:case_study:p_H:6}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/p_HgEC/p_HgEC[0][6].pdf}
		\caption{$P(h_{6} \vert e_{0}, c_{1})$ - \acs{Adam}}
		\label{fig:results:case_study:p_HgEC:0:6}
	\end{subfigure}
	\par\bigskip
	\caption{The average value of the concentration parameter $\boldsymbol{\alpha}$, at indices 0, 6, 7, and 8 over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study}
\end{figure}

@@

The first logical observation to be made from Figures \ref{fig:results:case_study:alphas:0} to \ref{fig:results:case_study:alphas:8} is the step-wise, increasing nature of $\boldsymbol{\alpha}$ for the bhh\_replay\_250 configuration, illustrated in \textcolor{green}{green}. Since the replay window size is sufficiently large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics at all. The value for $\boldsymbol{\alpha}$ is never reset to its initial value of 1.0, and thus, $\boldsymbol{\alpha}$ continues to increase throughout the training process. However, it should be noted that the rate and degree of change is different for different indices of $\boldsymbol{\alpha}$.

@@

@@

The probability distribution of heuristic selection probabilities is denoted by $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, where $\boldsymbol{\theta} \sim Dir(\boldsymbol{\alpha, K})$ are the sampled heuristic selection probabilities.

@@

@@

@@

The prior heuristic selection probability distribution is denoted $P(\boldsymbol{H} \vert \boldsymbol{\theta})$. As such, $P(\boldsymbol{H} \vert \boldsymbol{\theta}) = \boldsymbol{\theta}$ and heuristics are initially sampled such that $\boldsymbol{H} \sim Cat(\boldsymbol{\theta})$.

@@

@@

The posterior heuristic selection probability distribution is defined as $P(\boldsymbol{H} \vert \boldsymbol{E}, \boldsymbol{C}; \boldsymbol{\theta}, \boldsymbol{\phi}, \boldsymbol{\psi})$, where $\boldsymbol{E}$ represents the vector of entities in the entity pool, and $\boldsymbol{C}$ represents the vector of credit allocation outcomes as implemented by the credit assignment strategy. Furthermore $\boldsymbol{\theta}$ and $\boldsymbol{\phi}$ represent the probability distributions of heuristic selection probabilities and the entity selection probabilities respectively. Finally, $\boldsymbol{\psi}$ represents the probability distribution of successful credit allocation probabilities.

@@

@@
